### 2011-09-19 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

\chapter{Analysis of Recent Approaches}
\todo[inline]{bibref na prehladovy clanok?}
Approaches of XML schema inference can be divided by several criteria. A basic division is by the language the resulting schema is written in. Commonly used languages are DTD and XML Schema.

@@

According to my best knowledge at the time of writing there is just one approach of this category. It utilizes a set of XQuery queries to discover keys and foreign keys\todo{ref do literatury? Ty by tady něškodily všude, u každé té kategorie.}.

>>>>

\chapter{Analysis of Recent Approaches}
Approaches of XML schema inference can be divided by several criteria. A basic division is by the language the resulting schema is written in. Commonly used languages are DTD and XML Schema.

@@

According to our best knowledge at the time of writing there is just one approach of this category. It utilizes a set of XQuery queries to discover keys and foreign keys\todo{ref do literatury? Ty by tady něškodily všude, u každé té kategorie.}.
